---
title: "lab_report_knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(heleramcar6)
```


# Introduction
The Knapsack Problem is a classic combinatorial optimization problem. Given a set of items with weights and values, the goal is to determine the combination of items that maximizes the total value without exceeding a maximum weight capacity.
 
In this vignette, we will explore how to solve the Knapsack Problem using different approaches:

* *Brute Force*: Testing all possible combinations of items.
* *Greedy Heuristic*: A fast but suboptimal approximation.
* *Dynamic Programming*: An efficient approach for finding the optimal solution.


# Dataset
The library also includes an auxiliary function for creating a dummy knapsack dataset.

```{r}
knapsack_objects <- create_knapsack_objects()
```


# Questions

Using the function `system.time` (which returns the difference between two proc.time calls,
one before executing the given expression and the other one after), we were able to answer each
of the following questions regarding the time of execution for every solver.


## Question: How much time does it takes to run the brute forece algorithm for n = 16 objects?

```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:16, ], W = 3500))
```


## Question: How much time does it take to run the dynamic algorithm for n = 500 objects?

```{r}
system.time(knapsack_dynamic(x = knapsack_objects[1:500, ], W = 3500))
```

## Question: How much time does it takes to run the greedy algorithm for n = 1000000 objects?

```{r}
system.time(greedy_knapsack(x = knapsack_objects[1:1000000, ], W = 3500))
```


## Question: What performance gain could you get by parallelizing brute force search??

Using every available core in MacBook Pro M3 (`numcores <- parallel::detectCores()`) the 
time reduction using `n = 20` and `W = 3500` was from 23 seconds to 8. 
That is, an improvement of 65%.

However, while bulding the vignette using `devtools::check`, the following error was raised: 
`11 simultaneous processes spawned`. Further investigation revelead that CRAN limits the 
number of cores available to packages to 2 for performance reasons. So, for the purpose
of the execution of this vignette, that is what we do. Nonetheless, this probably won't 
show the results previously mentioned (65% time improvement). 

```{r}
system.time(brute_force_knapsack(x = knapsack_objects[1:15, ], W = 3500, parallel = FALSE))
```

```{r}
options(mc.cores = 2)
system.time(brute_force_knapsack(x = knapsack_objects[1:15, ], W = 3500, parallel = TRUE, numcores = 2))
```